Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-07-03 paper/Draft.tex
Made two corrections.

			\hline 
			Individual Moments                                  & Population Moments                             \\
			\hline 
			Mean forecast: $y_{i,t+h|t}$                   & Average forecast: $\bar y_{t+h|t}$                   \\
			Forecast error: $FE_{i,t+h|t}$ & Average forecast error: $\overline{FE}_{t+h|t}$ \\
			Uncertainty: $\sigma^2_{i,t+h|t}$         & Average uncertainty:  $\bar \sigma^2_{i,t+h|t}$ \\
			& Disagreements:  $\overline{Disg}_{t+h|t}$       \\
			\hline 
		\end{tabular}
	\end{table}

@@

	\begin{figure}[ht]
		\centering
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Realized Inflation and Uncertainty}
			\label{InfVar}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSCEM.png}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_PCE_varSPFPCEQ.png}
		\end{subfigure}
	    \vspace{1em}
		\vfill
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Forecast Errors and Uncertainty}
			\label{FEVar}
			\includegraphics[width=0.3\textwidth]{figures/SPFCPI_FE_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/SPFPCE_FE_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/SCE_FE_varSCEM.png}
		\end{subfigure}
	 \vspace{0.5em}
		\vfill
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Disagreements and Uncertainty}
			\label{DisgVar}
			\includegraphics[width=0.3\textwidth]{figures/CPI_disg_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/PCE_disg_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Q9_disg_varSCEM.png}\\
		\end{subfigure}
		\\
		\begin{flushleft}
			{\footnotesize Note:  From left to right: SPF’s CPI, SPF’s PCE, and SCE’s CPI forecast. From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of -0.10, -0.05 and -0.24, respectively; uncertainty (red dash) versus forecast errors (blue dot) with correlation coefficient of 0.13, 0.06, 0.40, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.29, -0.46 and 0.62. }
		\end{flushleft}
		\caption{Uncertainty and Other Moments}
		\label{UnceratitnyOtherMoments}
	\end{figure}

>>>>

			\hline 
			Individual Moments                                  & Population Moments                             \\
			\hline 
			Mean forecast: $y_{i,t+h|t}$                   & Average forecast: $\bar y_{t+h|t}$                   \\
			Forecast error: $FE_{i,t+h|t}$ & Average forecast error: $\overline{FE}_{t+h|t}$ \\
			Uncertainty: $\sigma^2_{i,t+h|t}$         & Average uncertainty:  $\bar \sigma^2_{t+h|t}$ \\
			& Disagreements:  $\overline{Disg}_{t+h|t}$       \\
			\hline 
		\end{tabular}
	\end{table}

@@

	\begin{figure}[ht]
		\centering
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Realized Inflation and Uncertainty}
			\label{InfVar}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_PCE_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSCEM.png}
		\end{subfigure}
	    \vspace{1em}
		\vfill
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Forecast Errors and Uncertainty}
			\label{FEVar}
			\includegraphics[width=0.3\textwidth]{figures/SPFCPI_FE_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/SPFPCE_FE_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/SCE_FE_varSCEM.png}
		\end{subfigure}
	 \vspace{0.5em}
		\vfill
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Disagreements and Uncertainty}
			\label{DisgVar}
			\includegraphics[width=0.3\textwidth]{figures/CPI_disg_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/PCE_disg_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Q9_disg_varSCEM.png}\\
		\end{subfigure}
		\\
		\begin{flushleft}
			{\footnotesize Note:  From left to right: SPF’s CPI, SPF’s PCE, and SCE’s CPI forecast. From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of -0.10, -0.05 and -0.24, respectively; uncertainty (red dash) versus forecast errors (blue dot) with correlation coefficient of 0.13, 0.06, 0.40, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.29, -0.46 and 0.62. }
		\end{flushleft}
		\caption{Uncertainty and Other Moments}
		\label{UnceratitnyOtherMoments}
	\end{figure}

### 2019-07-03 slides/ExpSlidesAfterDraft.tex
Made two corrections.

\documentclass{beamer}
\usepackage{default}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{adjustbox}  % Allows for fitting tables into slide

\usepackage{threeparttable}
\usepackage{caption}
\usepackage{subcaption}

@@

\title{Understanding Expectation Formation from Probabilistic Surveys}

@@

\begin{frame}{What I am doing}
\begin{itemize}
	\item Use \textcolor{blue}{density information} to 
	\begin{itemize}
		\item test expectation rigidity models 
		\item ... and identify differences in various theories 
	\end{itemize}
	\item Both \textcolor{blue}{individual} and population moments 
	\item \textcolor{blue}{Households} and professional forecasters 
	\begin{itemize}
		\item drivers of difference in rigidity across two types of agents
	\end{itemize}
	%\item Focus on aggregate variable inflation first, and then try \textcolor{blue}{individual variables} 
\end{itemize}
\end{frame}

@@

%
%\begin{frame}{Objections}
%\begin{itemize}
%	\item ``Subjective surveys are not trustworthy'' 
%	\begin{itemize}
%		\item Actually carefully designed. \cite{armantier2017overview}
%	\end{itemize}
%	\item ``People are bad at answering surveys, and worse on probabilities''  
%	\begin{itemize}
%		\item Not that bad. \cite{manski2004measuring}, \cite{delavande2014probabilistic}
%		\item Better than not.
%	\end{itemize}
%	\item ``A single parameter is enough for matching macro dynamics''
%	\begin{itemize}
%		\item No, heterogeneity in expectation could interact with other characteristics. 
%	\end{itemize}
%\end{itemize}
%\end{frame}

\begin{frame}{Literature}
\begin{itemize}
	\item \textbf{Theory}
	\begin{itemize}
		\item Sticky expectation \cite{carroll2003macroeconomic}, \cite{reis2006inattentive}
		\item Rational inattention \cite{sims2003implications},  \cite{gabaix2014sparsity}
		\item Noisy information \cite{lucas1972expectations}, \cite{woodford2001imperfect}
	\item Learning \cite{evans2012learning}
	\item Strategic interaction \cite{morris2002social}, \cite{hellwig2009knowing}
	\item Diagostic expectation  \cite{bordalo2018diagnostic}
	\item Model uncertainty \cite{hansen2001robust}, \cite{hansen2008robustness}
	\end{itemize}
\item \textbf{Empirics}
\begin{itemize}
	\item \textbf{Heterogeneity in Expectation:} \cite{mankiw2003disagreement}
	\item \textbf{Testing Theories:}  \textcolor{blue}{\cite{coibion2012can}, \cite{fuhrer2018intrinsic}}
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{eqnarray*}
	\widehat f_{i,t}(y_{t+h}|I_{i,t})
\end{eqnarray*}

\begin{itemize}
	\item Theories differ in $I_{i,t}$
	\item May also differ on information processing, i.e. $I_{i,t} \rightarrow \widehat f_{i,t}$
\end{itemize}

@@

\begin{frame}{Definition and notation}
\begin{itemize}
	\item \textcolor{red}{Individual}
	\begin{itemize}
		\item  mean forecast $\quad E_{i,t}(y_{t+h})$
		\item forecast error $\quad FE_{i,t+h|t} = y_{t+h}- E_{i,t}(y_{t+h})$
		\item \textcolor{blue}{uncertainty} $\quad Var_{i,t}(y_{t+h})$
	\end{itemize}
	\item \textcolor{red}{Population}
	\begin{itemize}
		\item average forecast  $\quad \bar E_{t}(y_{t+h})$
		\item average forecast error $\quad \overline {FE}_{t}= y_{t+h}-\bar E_{t}(y_{t+h})$
		\item \textcolor{blue}{cross-section disagreements}  $\quad Var_t(E_{i,t}(y_{t+h}))$
		\item \textcolor{blue}{average uncertainty}  $\quad \overline{Var}_t(y_{t+h})$
	\end{itemize}
\end{itemize}

@@

@@

\begin{frame}{Sticky Expectation: assumptions}
\begin{itemize}
	\item At time $t$, agent $i$ learns about $y_t$ at a fixed Poisson rate $\lambda$ 
	\item A non-updater since $t-\tau$  
	$$E_{i,t}(y_{t+h}|y_{t-\tau}) =\rho^{h+\tau} y_{t-\tau} $$
	\item An updater is a special cae  $\tau=0$ 
\end{itemize}
\end{frame}

$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
$$\textrm{SE} \quad \quad  \lambda = 0.4 $$ 
\begin{figure}
	\includegraphics[scale=0.25]{figuresDraft/ir_indse} 
\end{figure}
\end{frame}

$$\textrm{True Process} \quad  \rho=0.9, \quad \sigma_\omega=0.1, \quad \omega_1 = 0.1$$
$$\textrm{SE} \quad \quad  \lambda = 0.4 $$

\begin{figure}
	\includegraphics[scale=0.25]{figuresDraft/ir_popse} 
\end{figure}

@@

@@

$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 0.1, \quad \omega_1 = 0.1$$
$$ \textrm{SE:} \quad  \lambda = 0.5; \quad \textrm{NI:} \quad \sigma_\xi = 0.1, \quad \sigma_\epsilon = 0.1$$

\begin{figure}
	\includegraphics[height=6.3cm,width=10cm]{figuresDraft/ir_indseni} 
\end{figure}

@@

$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 0.1, \quad \omega_1 = 0.1$$
$$ \textrm{SE:} \quad  \lambda = 0.5; \quad \textrm{NI:} \quad \sigma_\xi = 0.1, \quad \sigma_\epsilon = 0.1$$

\begin{figure}
	\includegraphics[height=6.3cm,width=10cm]{figuresDraft/ir_popseni} 
\end{figure}

@@

\begin{frame}{A detailed look into noisy information}

\begin{figure}
	\includegraphics[height=8cm,width=8cm]{figuresDraft/ni_illustration} 
\end{figure}

\begin{frame}{Implied rigidity of different models}

@@

\begin{itemize}
	\item\cite{coibion2012can}
	\begin{itemize}
		\item \textcolor{blue}{FEs} respond to shocks and serially correlated. 
	\end{itemize}
	\item \textbf{Additional in this paper}
	\begin{itemize}
		\item \textcolor{blue}{Uncertainty} does not depend on shocks; and serially correlated. 
	\end{itemize}
\end{itemize}

@@

\begin{frame}{Identification strategies 2: differentiating theories}
\begin{itemize}
	\item\cite{coibion2012can}
	\begin{itemize}
		\item \textcolor{blue}{FEs} do not depend on past realizations according to baseline SE and NI; but do so according to heterogeneous priors or precision models. 
		\item Implied rigidity does not differ across shocks according to SE but differs according to NI. 
		\item \textcolor{blue}{Disagreements} rise after shocks according to baseline SE, strategic interactions and heterogeneous priors but invariant according to baseline NI.
	\end{itemize}
	\item \textbf{Additional in this paper}
	\begin{itemize}
		\item \textcolor{blue}{Uncertainty} do not depend on shocks per se according to baseline SE and NI, instead on degree of information rigidity.
	\end{itemize}
\end{itemize}

@@

\item \textbf{Density Estimation}: generalized beta estimation, \cite{engelberg2009comparing}
 \item \textbf{Identification of Shocks}: following \cite{coibion2012can} and monetary policy shocks. 
\end{itemize}

@@

	\begin{adjustbox}{width=0.9\textwidth}
	\begin{threeparttable}
		\label{RevEfficiency}
		\begin{tabular}{lllllllll}
			\hline 
			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
			\hline 
			\multicolumn{9}{l}{Test 1.  Revision efficiency of mean forecast}            \\
			\hline 
			& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
			\hline 
			L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  \\
			&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   \\
			L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  \\
			&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   \\
			L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     \\
			&               &           &          & (0.048)  &               &           &           & (0.069)   \\
			SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           \\
			&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           \\
			SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** \\
			&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   \\
			& -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   \\
			Constant & (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   \\
			\hline 
			N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       \\
			$R^2$                  & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     \\
			\hline 
		\end{tabular} 
		\begin{tablenotes}
			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
		\end{tablenotes}
	\end{threeparttable}
\end{adjustbox}

@@

\begin{adjustbox}{width=0.9\textwidth}
	\begin{threeparttable}
		\label{RevEfficiency}
		\begin{tabular}{lllllllll}
			\hline 
			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
			\hline 
			\multicolumn{9}{l}{Test 2. Revision efficiency of uncertainty}                                                            \\
			\hline 
			& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
			\hline 
			L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    \\
			&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   \\
			L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    \\
			&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   \\
			L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    \\
			&               &           &          & (0.121)  &               &           &           & (0.149)   \\
			Constant              & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   \\
			& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   \\
			\hline 
			N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       \\
			$R^2$                 & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723    \\
			\hline 
		\end{tabular} 
		\begin{tablenotes}
			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
		\end{tablenotes}
	\end{threeparttable}
\end{adjustbox}

@@

	\begin{adjustbox}{width=\textwidth}
	\begin{threeparttable}
		\caption{Weak Tests of Revision Efficiency using Change in Forecasts and Uncertainty}
		\label{WeakRevEfficiency}
		\begin{tabular}{llllllllllllll}
			\hline 
			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
			\hline 
			\multicolumn{14}{l}{Test 3. Weak revision efficiency of change in forecast}                                                                                                                                    \\
			\hline 
			& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
			\hline 
			L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Mean\_ch  &         & -0.433*** & -0.586*** & -0.642*** \\
			&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                    &         & (0.01)     & (0.013)    & (0.025)    \\

@@

				\label{WeakRevEfficiency}

@@

\begin{frame}{Results from \cite{coibion2012can}}

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/CPIAU_ashocks_before2007.png}  \\
	\smallskip 
	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFFE_ashocks_before2007.png} \\
	\smallskip
	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFDisg_ab_ashocks_before2007.png} 
\end{figure}

@@

\begin{figure}
	\includegraphics[width=7cm]{figuresDraft/Inf_ashocks.png} 
	\smallskip
	\includegraphics[width=7cm]{figuresDraft/SPFFE_ashocks.png} \\
	\smallskip
	\includegraphics[width=7cm]{figuresDraft/SPFDisg_ab_ashocks.png} 
	\smallskip
	\includegraphics[width=7cm]{figuresDraft/SPFVar_ab_ashocks.png}  
\end{figure}

@@

\begin{figure}
	\includegraphics[width=7cm]{figuresDraft/Inf_ashocks_nmp.png}

	\includegraphics[width=7cm]{figuresDraft/SPFFE_ashocks_nmp.png}  \\
	\smallskip 
	\includegraphics[width=7cm]{figuresDratf/SPFDisg_ab_ashocks_nmp.png} 
	\smallskip 
	\includegraphics[width=7cm]{figuresDraft/SPFVar_ab_ashocks_nmp.png}  
\end{figure}

>>>>

\documentclass{beamer}
\usepackage{default}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{adjustbox}  % Allows for fitting tables into slide
\usepackage{hyperref}
\usepackage{threeparttable}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{natbib}

@@

\title{Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households}

@@

\begin{frame}{What this paper does?}
\begin{itemize}
	\item Use \textcolor{blue}{uncertainty} from density forecasts to 
	\begin{itemize}
		\item test models of expectation rigidity 
		\item ... and identify differences in various theories 
	\end{itemize}
	\item Both \textcolor{blue}{individual} and population moments 
	\item \textcolor{blue}{Households} and professional forecasters 
	\begin{itemize}
		\item drivers of difference in rigidity across two types of agents
	\end{itemize}
	%\item Focus on aggregate variable inflation first, and then try \textcolor{blue}{individual variables} 
\end{itemize}
\end{frame}

@@

%
%\begin{frame}{Objections}
%\begin{itemize}
%	\item ``Subjective surveys are not trustworthy'' 
%	\begin{itemize}
%		\item Actually carefully designed. \citet{armantier2017overview}
%	\end{itemize}
%	\item ``People are bad at answering surveys, and worse on probabilities''  
%	\begin{itemize}
%		\item Not that bad. \citet{manski2004measuring}, \citet{delavande2014probabilistic}
%		\item Better than not.
%	\end{itemize}
%	\item ``A single parameter is enough for matching macro dynamics''
%	\begin{itemize}
%		\item No, heterogeneity in expectation could interact with other characteristics. 
%	\end{itemize}
%\end{itemize}
%\end{frame}

\begin{frame}{Literature}
\begin{itemize}
	\item \textbf{Testing theories of expectation formation}
	\item \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}. 
	\item  \citet{coibion2018firms} 
	\item  \citet{malmendier2015learning}, \citet{das2017socioeconomic}
	\item \textcolor{blue}{\citet{coibion2012can} and \citet{fuhrer2018intrinsic}}
\end{itemize}

@@

\begin{eqnarray*}
	f_{i,t+h|t} \equiv f_{i,t}(y_{t+h}|I_{i,t})
\end{eqnarray*}

\begin{itemize}
	\item Theories differ in $I_{i,t}$
	\item May also differ on information processing, i.e. $I_{i,t} \rightarrow f_{i,t+h|t}$, i.e. heterogeneous models and priors. \citet{patton2010forecasters}.
\end{itemize}

@@

\begin{frame}{Definition and notation}
	\begin{table}[ht]
	\centering
	\caption{Definition and Notation of Moments}
	\label{MomSum}
	\begin{tabular}{ll}

		\hline 
		Individual Moments                                  & Population Moments                             \\
		\hline 
		Mean forecast: $y_{i,t+h|t}$                   & Average forecast: $\bar y_{t+h|t}$                   \\
		Forecast error: $FE_{i,t+h|t}$ & Average forecast error: $\overline{FE}_{t+h|t}$ \\
		Uncertainty: $\sigma^2_{i,t+h|t}$         & Average uncertainty:  $\bar \sigma^2_{i,t+h|t}$ \\
		& Disagreements:  $\overline{Disg}_{t+h|t}$       \\
		\hline 
	\end{tabular}
\end{table}

@@

\subsection{Full-information Rational Expectation(FIRE)}

\begin{frame}{Full-information rational expectation: assumptions}
\begin{itemize}
	\item $y_t$ is perfectly observed in each period
	\item All agents understand and agree on the process 
\end{itemize}
\end{frame}

\begin{frame}{FIRE: predictions}
\begin{itemize}
	\item  $$\overline{FE}^{*}_{i,t+h|t} = \sum^{h}_{k=1} \rho^k \omega_{t+k}$$
	\item  $$\bar \sigma^{*2}_{t+h|t} = \sum^{h}_{s=1}\rho^{2s} \sigma^2_{\omega}$$
	\item 	
	$$\bar \sigma^{*2}_{t+h|t+1} - \bar \sigma^{*2}_{t+h|t}  =  \rho (\bar \sigma^{*2}_{t+h|t} - \bar \sigma^{*2}_{t+h|t-1})$$
\end{itemize}
\end{frame}

@@

\begin{frame}{Sticky Expectation: assumptions}
\begin{itemize}
	\item At time $t$, agent $i$ learns about $y_t$ at a fixed Poisson rate $\lambda$ 
	\item A non-updater since $t-\tau$  
	$$y_{i,t+h|t-\tau}=\rho^{h+\tau} y_{t-\tau} $$
	\item An updater is a special case  $\tau=0$ 
\end{itemize}
\end{frame}

@@

\begin{frame}{An illustration of noisy information}

\begin{figure}
	\includegraphics[height=0.8\textheight,width=\textwidth]{figuresDraft/ni_illustration} 
\end{figure}

@@

$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 1, \quad \omega_t = 1$$
$$ \textrm{SE:} \quad  \lambda = 0.25; \quad \textrm{NI:} \quad \sigma_\xi =  \sigma_\epsilon = \sigma_y$$

\begin{figure}
	\includegraphics[height=0.6\textheight,width=\textwidth]{figuresDraft/ir_indseni} 
\end{figure}

@@

$$\textrm{True Process} \quad   \rho=0.9, \quad \sigma_\omega= 1, \quad \omega_t = 1$$
$$ \textrm{SE:} \quad  \lambda = 0.25; \quad \textrm{NI:} \quad \sigma_\xi =  \sigma_\epsilon = \sigma_y$$

\begin{figure}
	\includegraphics[height=0.6\textheight,width=\textwidth]{figuresDraft/ir_popseni} 
\end{figure}

@@

\begin{frame}{Comparing FIRE, SE and NI}

@@

\begin{itemize}
	\item \citet{coibion2012can}
	\begin{itemize}
		\item \textcolor{blue}{FEs} respond to shocks and serially correlated. 
	\end{itemize}
	\item \textbf{Additional in this paper}
	\begin{itemize}
		\item \textcolor{blue}{Uncertainty} does not depend on shocks; and serially correlated. 
	\end{itemize}
\end{itemize}

@@

\begin{frame}{Identification strategies 2: differentiating theories}
\begin{itemize}
	\item \citet{coibion2012can}
	\begin{itemize}
		\item \textcolor{blue}{FEs} do not depend on past realizations according to baseline SE and NI; but do so according to heterogeneous priors or precision models. 
		\item Implied rigidity does not differ across shocks according to SE but differs according to NI. 
		\item \textcolor{blue}{Disagreements} rise after shocks according to baseline SE, strategic interactions and heterogeneous priors but invariant according to baseline NI.
	\end{itemize}
	\item \textbf{Additional in this paper}
	\begin{itemize}
		\item \textcolor{blue}{Uncertainty} do not depend on shocks per se according to baseline SE and NI, instead on degree of information rigidity.
	\end{itemize}
\end{itemize}

@@

\item \textbf{Density Estimation}: generalized beta estimation, \citet{engelberg2009comparing}
 \item \textbf{Identification of Shocks}: following \citet{coibion2012can} and monetary policy shocks. 
\end{itemize}

@@

	\begin{adjustbox}{width=0.9\textwidth}
	\begin{threeparttable}
		\label{MeanRevEfficiency}
		\begin{tabular}{lllllllll}
			\hline 
			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
			\hline 
			\multicolumn{9}{l}{Test 1.  Revision efficiency of mean forecast}            \\
			\hline 
			& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
			\hline 
			L.InfExp\_Mean\_rv  &               & 0.539***  & 0.418*** & 0.387*** &               & 0.606***  & 0.435***  & 0.369***  \\
			&               & (0.031)   & (0.043)  & (0.052)  &               & (0.034)   & (0.042)   & (0.049)   \\
			L2.InfExp\_Mean\_rv &               &           & 0.218*** & 0.166**  &               &           & 0.261***  & 0.246***  \\
			&               &           & (0.040)  & (0.053)  &               &           & (0.047)   & (0.058)   \\
			L3.InfExp\_Mean\_rv &               &           &          & 0.134**  &               &           &           & 0.116     \\
			&               &           &          & (0.048)  &               &           &           & (0.069)   \\
			SPFCPI\_ct50        &               & -0.444*** & -0.391** & -0.454** &               &           &           &           \\
			&               & (0.105)   & (0.124)  & (0.138)  &               &           &           &           \\
			SPFPCE\_ct50        &               &           &          &          &               & -0.432*** & -0.413*** & -0.504*** \\
			&               &           &          &          &               & (0.109)   & (0.111)   & (0.138)   \\
			& -1.257***     & 0.329     & 0.351    & 0.546*   & -1.095***     & 0.365     & 0.428*    & 0.641**   \\
			Constant & (0.045)       & (0.191)   & (0.237)  & (0.269)  & (0.039)       & (0.188)   & (0.191)   & (0.228)   \\
			\hline 
			N                   & 1337          & 1045      & 822      & 652      & 1111          & 867       & 683       & 549       \\
			$R^2$                  & 0.000         & 0.335     & 0.355    & 0.372    & 0.000         & 0.409     & 0.444     & 0.452     \\
			\hline 
		\end{tabular} 
		\begin{tablenotes}
			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
		\end{tablenotes}
	\end{threeparttable}
\end{adjustbox}

@@

\begin{adjustbox}{width=0.9\textwidth}
	\begin{threeparttable}
		\label{VarRevEfficiency}
		\begin{tabular}{lllllllll}
			\hline 
			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       \\
			\hline 
			\multicolumn{9}{l}{Test 2. Revision efficiency of uncertainty}                                                            \\
			\hline 
			& Mean revision & t-1       & t-1- t-2 & t-1-t-3  & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
			\hline 
			L.InfExp\_Var\_rv   &               & 0.290*    & 0.529*** & 0.581*** &               & 0.577***  & 0.477***  & 0.344*    \\
			&               & (0.122)   & (0.117)  & (0.145)  &               & (0.080)   & (0.130)   & (0.148)   \\
			L2.InfExp\_Var\_rv  &               &           & -0.059   & -0.209   &               &           & 0.360*    & 0.205*    \\
			&               &           & (0.125)  & (0.127)  &               &           & (0.143)   & (0.098)   \\
			L3.InfExp\_Var\_rv  &               &           &          & 0.353**  &               &           &           & 0.390*    \\
			&               &           &          & (0.121)  &               &           &           & (0.149)   \\
			Constant              & -0.034***     & -0.011**  & -0.008*  & -0.005   & -0.039***     & -0.019**  & -0.010**  & -0.007*   \\
			& (0.005)       & (0.004)   & (0.003)  & (0.004)  & (0.006)       & (0.006)   & (0.003)   & (0.003)   \\
			\hline 
			N                   & 1189          & 877       & 663      & 504      & 1082          & 801       & 604       & 458       \\
			$R^2$                 & 0.000         & 0.124     & 0.284    & 0.408    & 0.000         & 0.353     & 0.583     & 0.723    \\
			\hline 
		\end{tabular} 
		\begin{tablenotes}
			\item Standard errors are clustered by date. *** p$<$0.001, ** p$<$0.01 and * p$<$0.05.
		\end{tablenotes}
	\end{threeparttable}
\end{adjustbox}

@@

	\begin{adjustbox}{width=\textwidth}
	\begin{threeparttable}
		\caption{Weak Tests of Revision Efficiency using Change in Forecasts and Uncertainty}
		\label{MeanWeakRevEfficiency}
		\begin{tabular}{llllllllllllll}
			\hline 
			& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
			\hline 
			\multicolumn{14}{l}{Test 3. Weak revision efficiency of change in forecast}                                                                                                                                    \\
			\hline 
			& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
			\hline 
			L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Mean\_ch  &         & -0.433*** & -0.586*** & -0.642*** \\
			&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                    &         & (0.01)     & (0.013)    & (0.025)    \\

@@

				\label{VarWeakRevEfficiency}

@@

\begin{frame}{Results from \citet{coibion2012can}}

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/CPIAU_ashocks_before2007.png}  \\
	\smallskip 
	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFFE_ashocks_before2007.png} \\
	\smallskip
	\includegraphics[width=0.5\textwidth,totalheight=0.28\textheight]{figuresDraft/SPFDisg_ab_ashocks_before2007.png} 
\end{figure}
\end{frame}

@@

\begin{figure}
	\includegraphics[width=0.6\textwidth,totalheight=\0.4\textheight]{figuresDraft/Inf_ashocks_nmp.png}  
	\includegraphics[[width=0.6\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFFE_ashocks_nmp.png}  \\
	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFDisg_ab_ashocks_nmp.png} 
	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFVar_ab_ashocks_nmp.png}  
\end{figure}
\end{frame}

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/Inf_ashocks.png} 
	\smallskip
	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFFE_ashocks.png} \\
	\smallskip
	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFDisg_ab_ashocks.png} 
	\smallskip
	\includegraphics[width=0.5\textwidth,totalheight=\0.4\textheight]{figuresDraft/SPFVar_ab_ashocks.png}  
\end{figure}
